\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage[paper=a4paper,left=3cm, right=3cm, top=2cm]{geometry}
\usepackage{blindtext}
\usepackage{multicol}
\usepackage{pgfplots}
\usepackage{float}
\usepackage{biblatex} %Imports biblatex package
\usepackage{amsmath}
\pgfplotsset{compat = newest}

\title{\textbf{Recent Development in inorganic scintillator-based optic fiber dosimeters}}
\author{Neelkant Newra \\ \textit{Department of Biomedical Engineering} \\ National Institute of Technology, Raipur \\ Email: newra008@gmail.com}

\begin{document}

\maketitle

\section*{Aim}
To study the various development in the area of Scintillator-based optic fiber dosimeter, concentrating especially on the inorganic Scintillator. 
\section*{Keywords}

\begin{enumerate}
    \item \textbf{Scintillator:}  a material that fluoresces when struck by a charged particle or high-energy photon.  
    \item \textbf{Scintillation:}  the process or state of emitting flashes of light.
     \item \textbf{Optical fiber:}  a thin flexible fibre with a glass core through which light signals can be sent with very little loss of strength.
     \item \textbf{Dosimeters:}  It is a device that measures dose uptake of external ionizing radiation.
     \item \textbf{Dosimetry:}  Radiation dosimetry in the fields of health physics and radiation protection is the measurement, calculation and assessment of the ionizing radiation dose absorbed by an object, usually the human body.
     \item \textbf{Radiation:}  the emission of energy as electromagnetic waves or as moving subatomic particles, especially high-energy particles which cause ionization.
     
\section*{Task}

\begin{itemize}
    \item Looked for the various review paper published in the domain of our research. 
    \item Extracting the research paper from such review paper, specifically targeting inorganic Scintillator. 
    \item Developing the table, consisting of the Scintillator, its density,efficiency, maximum eEmission, decay time. 
\end{itemize} 
     
    
\end{enumerate}
\end{document}

